`r params$doc_title`

### 2023-05-09 scripts/MSc.Rmd
highlighted best methods in barplots

    df.temp.long[[ref.method]] %>%
      mutate(N=paste0("Sample Size: ", format(N, scientific=FALSE))) %>% 
      mutate(label.too.large = ifelse(mse>my.y.lim, paste0("MSE \u2265 ", my.y.lim) , NA)) %>%
      filter(Scenario == scenarios[scenario]) %>% 
      ## DROP NA (e.g. no sample sizes 50.000)
      drop_na(Mean) %>%  
      group_by(N) %>% 
      mutate(smallest_mse = mse == min(mse)) %>% # add a new column to identify the rows with the smallest mse value within each group
      ungroup() %>% 
      # PLOT
      ggplot(aes(x=Method, y=mse)) +
      geom_bar(
        aes(fill = smallest_mse), # add fill aesthetics to highlight the bars with the smallest mse value within each group
        stat="identity", position=position_dodge2(reverse=TRUE),
        #color=ggthemes_data$few$colors$Dark[2,2][[1]],
        ) +   # reverse dodge
      geom_text(aes(x= Method, y= my.y.lim, label = label.too.large,
                    colour=label.too.large), #position = position_dodge(),
                nudge_y = -0.1, #size = 2.25, angle = 90
                color=ggthemes_data$few$colors$Dark[4,2][[1]],
                fontface="bold"
                )+
      facet_wrap(~N, nrow = 4) + 
      xlab("Method")+
      ylab(paste0("Mean Squared Error with nsim=", nsim))+
      labs(title = paste0("Selected Reference Method: ", 
                              selected_true_methods[ref.method]),
           subtitle = paste0("Genetic Architecture: ", scenarios[scenario])
           )+
      #ylim(0, 0.5)+
      coord_flip(ylim=c(0, my.y.lim))+
      ggthemes::theme_few()+  # remove legend
      ggthemes::scale_fill_few() -> dodged.barplot.mse.scenario[[scenario]]

@@

      if (SAVE.files ==TRUE ){
        ## arranged plots are toooo small 
        filename.dodged.barplot.mse.scenario <- paste0("./output/plots/summary-plots/scenario_",scenarios[scenario],"/",
                                              Sys.Date(), "_mse_GSD_dodged_barplot_REF_METHOD_",
                                              selected_true_methods[ref.method], "_NSIM_", nsim)
        ggsave(filename = paste0(filename.dodged.barplot.mse.scenario, ".svg"), 
               plot = dodged.barplot.mse.scenario[[scenario]], 
               width = 5, height = 8, 
               units = "in"  # default
               )
      }
  }
  dodged.barplot.mse.references[ref.method] <- dodged.barplot.mse.scenario[1]

  # scenarios without all instruments in arranged plot
  arrangedplot.mse.scenarios <- 
    ggarrange(plotlist = dodged.barplot.mse.scenario[-1], labels = c("A", "B", "C", "D", "E", "F"))
  plot(arrangedplot.mse.scenarios)
  if (SAVE.files ==TRUE ){
        ## arranged plots are toooo small 
        filename.arrangedplot.mse.scenarios <- paste0("./output/plots/summary-plots/arranged_scenarios/",
                                              Sys.Date(), "_mse_GSD_dodged_barplot_REF_METHOD_",
                                              selected_true_methods[ref.method], "_NSIM_", nsim)
        ggsave(filename = paste0(filename.arrangedplot.mse.scenarios, ".svg"), 
               plot = arrangedplot.mse.scenarios, 
               width = 10, height = 12, 
               units = "in"  # default
               )
  }

>>>>

    df.temp.long[[ref.method]] %>%
      mutate(N=paste0("Sample Size: ", format(N, scientific=FALSE))) %>% 
      mutate(label.too.large = ifelse(mse>my.y.lim, paste0("MSE \u2265 ", my.y.lim) , NA)) %>%
      filter(Scenario == scenarios[scenario]) %>% 
      ## DROP NA (e.g. no sample sizes 50.000)
      drop_na(Mean) %>%  
      group_by(N) %>% 
      mutate(smallest_mse = mse == min(mse)) %>% # add a new column to identify the rows with the smallest mse value within each group
      ungroup() %>% 
      # PLOT
      ggplot(aes(x=Method, y=mse)) +
      geom_bar(
        aes(fill = smallest_mse), # add fill aesthetics to highlight the bars with the smallest mse value within each group
        stat="identity", position=position_dodge2(reverse=TRUE),
        #color=ggthemes_data$few$colors$Dark[2,2][[1]],
      ) +   # reverse dodge
      geom_text(aes(x= Method, y= my.y.lim, label = label.too.large,
                    colour=label.too.large), #position = position_dodge(),
                nudge_y = -0.1, #size = 2.25, angle = 90
                color=ggthemes_data$few$colors$Dark[4,2][[1]],
                fontface="bold"
      )+
      facet_wrap(~N, nrow = 4) + 
      xlab("Method")+
      ylab(paste0("Mean Squared Error with nsim=", nsim))+
      labs(#title = paste0("Selected Reference Method: ", 
          #                selected_true_methods[ref.method]),
           #subtitle = paste0("Genetic Architecture: ", scenarios[scenario])
      )+
      #ylim(0, 0.5)+
      coord_flip(ylim=c(0, my.y.lim))+
      ggthemes::theme_few()+  # remove legend
      scale_fill_manual(values = c("gray80", "blue"), guide = "none") -> dodged.barplot.mse.scenario[[scenario]]

@@

      if (SAVE.files ==TRUE ){
        ## arranged plots are toooo small 
        filename.dodged.barplot.mse.scenario <- paste0("./output/plots/summary-plots/scenario_",scenarios[scenario],"/",
                                              Sys.Date(), "_mse_GSD_dodged_barplot_REF_METHOD_",
                                              selected_true_methods[ref.method], "_NSIM_", nsim)
        ggsave(filename = paste0(filename.dodged.barplot.mse.scenario, ".svg"), 
               plot = dodged.barplot.mse.scenario[[scenario]], 
               width = 5, height = 8, 
               units = "in"  # default
               )
      }
  }
  dodged.barplot.mse.references[ref.method] <- dodged.barplot.mse.scenario[1]   # save scenario 1 "ALL INSTR"

  # scenarios WITHOUT all instruments in arranged plot
  arrangedplot.mse.scenarios <- 
    ggarrange(plotlist = dodged.barplot.mse.scenario[-1], labels = c("A", "B", "C", "D", "E", "F"))
  plot(arrangedplot.mse.scenarios)
  if (SAVE.files ==TRUE ){
        ## arranged plots are toooo small 
        filename.arrangedplot.mse.scenarios <- paste0("./output/plots/summary-plots/arranged_scenarios/",
                                              Sys.Date(), "_mse_GSD_dodged_barplot_REF_METHOD_",
                                              selected_true_methods[ref.method], "_NSIM_", nsim)
        ggsave(filename = paste0(filename.arrangedplot.mse.scenarios, ".svg"), 
               plot = arrangedplot.mse.scenarios, 
               width = 10, height = 12, 
               units = "in"  # default
               )
  }
